TGI-spinal-power

### 2022-05-18 analysis/tgispine_zoib_power-sim.Rmd
fixing data so standard deviations are across particpants, not trials

# Summarise beta per rating, per condition for all participants (for simulations)
# mean
df_sum <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    mean, data = df_VAS)
setnames(df_sum, "beta", "mean")
# standard deviation
df_sd <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    SD, data = df_VAS)
setnames(df_sd, "beta", "std")
# merge
df_sum <- merge(df_sum, df_sd)

@@

# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)}
  # then run the model based on simulated data
  m <- model(df_csim, 'cold')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

# Then warm
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)}
  # then run the model based on simulated data
  m <- model(df_sim, 'warm')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

>>>>

# Summarise beta per rating, per condition, per participant
# median
df_sum_pp <- aggregate(beta~ID*manipulation*condition*cold_location*VAS, 
                    median, data = df_VAS)

# now summarise across participants
df_sum <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    mean, data = df_sum_pp)
setnames(df_sum, "beta", "mean")
# standard deviation
df_sd <- aggregate(beta~manipulation*condition*cold_location*VAS, 
                    SD, data = df_sum_pp)
setnames(df_sd, "beta", "std")
# merge
df_sum <- merge(df_sum, df_sd)

@@

# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'cold')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

# Then warm
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'warm')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}
